---
title: "The spread trend of covid-19 in Iraq"
---

Based on monthly data, I showed total cases, new cases, total deaths, new deaths, tests per case and positive rate of covid-19 in Iraq. As shown in Table 2 below, we can find that the spread of covid-19 seems to have reached a peak in April 2021. After that, the epidemic situation showed a trend of improvement in May and June. Unfortunately, since July, the epidemic in Iraq has repeatedly occurred, with new cases even reaching new highs.


```{r echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(DT)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
coviddata <- read.csv("owid-covid-data.csv",header = TRUE)
Iraq <- coviddata %>% filter(location=="Iraq")
Iraq_new <- Iraq %>% select(date,total_cases,new_cases,
                            total_deaths,new_deaths,tests_per_case,positive_rate)
Iraq_new <- na.omit(Iraq_new)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
Iraq_new$month <- substr(Iraq_new$date,1,7)
data <- Iraq_new %>%
  select(-date) %>%
  group_by(month) %>%
  summarise_all(mean)%>% 
  mutate_if(is.numeric, format, 3)
DT::datatable(data,caption = htmltools::tags$caption('Table 2: Mean of COVID-19 data by each month of Iraq.', style="color:black"),
              options = list(pageLength = 10,paging = FALSE,searching = FALSE,rownames= FALSE,
                             initComplete = JS(
                               "function(settings, json) {",
                               "$(this.api().table().header()).css({'background-color': '#336699','color': '#fff'});","}")))
```