---
title: "The spread trend of covid-19 in Russia"
---

## Introduction
At the previous page we had acquired some information about the spread trend in Iraq. And the new research will focus on the situation of covid-19 epidemic in Russia. We use the 
same dataset 

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(plotly)
```

## The increasing Trend of covid-19 in Russia 
```{r, echo=FALSE,message=FALSE,warning=FALSE}
covid_data <- read.csv("owid-covid-data.csv",header = TRUE)
Russia <- covid_data %>% filter(location=="Russia")
Russia_new <- Russia %>% select(date,total_cases,new_cases,
                            total_deaths,new_deaths,tests_per_case,
                            new_cases_per_million,
                            positive_rate,
                            new_tests_smoothed)
Russia_new <- na.omit(Russia_new)
```




```{r, echo=FALSE,message=FALSE,warning=FALSE}
plot_ly(Russia_new, x = ~date, color = I("black")) %>%
 add_lines(y = ~new_deaths) %>%
 add_lines(y = ~new_cases, color = I("orange"))
```
The line chart illustartes that the growth trend was slight at beginning , but the number of new cases per day began to rise sharply from September and peaked on December 24.
After taking some protection measures, the number of new cases had to declined. Unfortunately, good time doesn't last long, with COVID-19 spread in global again, the new
cases in Russia was increasing from May 2021. The new deaths per day has been stable even though the new cases is keep increasing.



## The positive rate of different days

```{r, echo=FALSE,message=FALSE,warning=FALSE}
pic <- plot_ly(Russia_new, x = ~date, y = ~new_tests_smoothed)
add_markers(pic, color  = ~positive_rate)
```



The scatterplot above has shown that how many people were tested every day and the 
positive rate of those people. We can clearly see that the positive rate is keeping 
from 0.02 to 0.04 for most of days. But in January 2021 the positive rate was raisen to 0.08.

